paper

### 2024-09-18 paper.qmd
.

>>>>

# Load the dataset
load("../LimROTS paper/metabolomics/BM21.Case3.rda")

print(BM21.Case3)

# Set metadata and formula for LimROTS analysis
meta.info <- c("mixing.ratio" , "fake.batch")
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case3)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30   # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio + fake.batch"  # Formula for group comparison

# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = BM21.Case3, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
```

load("../LimROTS paper/metabolomics/BM21.Case3.rda")

print("BM21.Case3")
data <- assay(BM21.Case3)
formula.str <- "~ 0 + mixing.ratio + fake.batch"
meta.info <- data.frame(colData(BM21.Case3), check.names = FALSE, row.names = row.names(colData(BM21.Case3)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("mixing.ratio1-mixing.ratio2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=T, robust=T)
limma.result <- topTable(fit.ebayes, coef="mixing.ratio1-mixing.ratio2" , number = "Inf")

limma.result <- limma.result[limma.result$adj.P.Val < 0.05,]

length(which(grepl("_pluseffect", row.names(limma.result)) ))

length(which(grepl("synthetic", row.names(limma.result)) ))
